Probability Distribution Checks

### 2017-07-23 Probability_distribution_checks.Rmd
Update Probability_distribution_checks.Rmd/md

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked. However, in these data only normal and exponential

@@

The 2016 data fit an exponential distribution while the 2016 data fit a normal distribution.

>>>>

Here we check the probability distribution that best fits these data. I'm
following a method from
http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
As you see in that guide, there are several distributions that can be checked.
However, in these data only normal and exponential are necessary.

@@

The 2015 data fit an exponential distribution while the 2016 data fit a normal
distribution.

### Leaf Sheath Blight Severity Distributions

The 2015 data contain negative values, so an exponential distribution will not
fit. The 2016 data fit a normal distribution better than exponential.

### Tiller Sheath Blight Severity Distributions

The 2015 data contain negative values, so an exponential distribution will not
fit. The 2016 data fit a normal distribution better than exponential.
